---
title: "140.615.HW.11.Jin.Vincent"
author: "Vincent Jin"
date: "2023-05-03"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Homework 11
## Vincent Jin

``` {r}
library(SPH.140.615)
copper <- copper
```

# 1.
The percent transmittance for a sample with unknown copper concentration was measured to be 35.6%. Use your fitted calibration line from the previous homework to estimate the copper concentration in this sample. Calculate a 95% confidence interval for the copper concentration in this sample. Make a figure (including the calibration line) that visualizes your results.

***Answer***

``` {r}
# regression line from previos homework
lm.fit <- lm(log10(response)~concentration, data = copper)

# Calibration
calibrate(copper$concentration, log10(copper$response), log10(35.6))

# Visualization
xx <- seq(1, 50, by = 0.1)
predict.new <- predict(lm.fit, data.frame(concentration=xx), interval="prediction")
predict.mean <- predict(lm.fit, data.frame(concentration=xx), interval="confidence")
plot(copper$concentration, log10(copper$response), xlab="x", ylab="y", ylim=range(predict.new), col="lightgrey")
lines(xx, predict.mean[,1], lwd=2)
lines(xx, predict.mean[,2], lty=2)
lines(xx, predict.mean[,3], lty=2)
lines(xx, predict.new[,2], lty=2, col="blue")
lines(xx, predict.new[,3], lty=2, col="blue")
```
