---
title: "140.615.HW.11.Jin.Vincent"
author: "Vincent Jin"
date: "2023-05-03"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Homework 11
## Vincent Jin

``` {r}
library(SPH.140.615)
copper <- copper
```

# 1.
The percent transmittance for a sample with unknown copper concentration was measured to be 35.6%. Use your fitted calibration line from the previous homework to estimate the copper concentration in this sample. Calculate a 95% confidence interval for the copper concentration in this sample. Make a figure (including the calibration line) that visualizes your results.

***Answer***

``` {r}
# regression line from previos homework
lm.fit <- lm(log10(response)~concentration, data = copper)

# Calibration
calibrate(copper$concentration, log10(copper$response), log10(35.6))

# Visualization
xx <- seq(1, 50, by = 0.1)
predict.new <- predict(lm.fit, data.frame(concentration=xx), interval="prediction")
predict.mean <- predict(lm.fit, data.frame(concentration=xx), interval="confidence")
plot(copper$concentration, log10(copper$response), xlab="concentration", ylab="log10(response)", ylim=range(predict.new), col="lightgrey")
lines(xx, predict.mean[,1], lwd=2)
lines(xx, predict.mean[,2], lty=2)
lines(xx, predict.mean[,3], lty=2)
lines(xx, predict.new[,2], lty=2, col="blue")
lines(xx, predict.new[,3], lty=2, col="blue")
```

The copper concentration in this sample may be 21.82 with a confidence interval (19.48, 24.17).

# 2.
The data for this problem are in the dat.xy data frame in the SPH.140.615 package. Here, X is the predictor, and Y is the response.

## (a)
Fit a regression line using the function lm, and provide estimates for the intercept $\beta_0$, the slope $\beta_1$, and the residual standard deviation $\sigma$.

***Answer***

``` {r}
xy <- dat.xy
lm.fit <- lm(Y ~ X, data = xy)
summary(lm.fit)
```

The $\beta_0$ is -227.31 and $\beta_1$ is 14.10. The residual standard deviation $\sigma$ is 80.88.

## (b)
Provide 95% confidence intervals for $\beta_0$ and $\beta_1$.

***Answer***

``` {r}
confint(lm.fit)
```

The confidence intervals for $\beta_0$ is (-472.60, 17.99), and for $\beta_1$ is (9.82, 18.38)

## (c)
Plot the data, and show the regression line.

***Answer***

``` {r}
plot(xy$X, xy$Y, xlab="X", ylab="Y")
abline(lm(xy$Y ~ xy$X), col="blue", lty=2)
```

## (d)
What is the expected response for X = 60? What is the expected response for X = 70? Provide 95% confidence intervals using the function predict.

***Answer***

``` {r}
predict(lm.fit, data.frame(X = c(60, 70)), interval = "confidence")
```

The expected response for X = 60 was 618.60 with a confidence interval of (591.88, 645.31) and for X = 70 was 759.58 with a confidence (699.30, 819.86).

## (e)
For both X = 60 and X = 70, also provide 95% prediction intervals.

***Answer***

``` {r}
predict(lm.fit, data.frame(X = c(60, 70)), interval = "prediction")
```

For X = 60 and 70 the prediction intervals are:  (453.615,783.578),  (585.974, 933.187) respectively.

## (f)
Comment on the lengths of the four intervals.

***Answer***

The prediction interval seems to be wider than the 95% confidence interval.

#3.
The data for this problem are in the fev data frame in the SPH.140.615 package. The response is a measure of lung function (FEV, in liters). The other variables are the gender of a subject (male/female), the height (in inches), and whether or not that person is a smoker (yes/no). Analyze the data using linear regression (note: there are no interactions in these data, so you don’t need to worry about them), and report your findings. In particular:

## (a)
Explore the data by plotting them in a meaningful way, and comment.

***Answer***

``` {r}
lm.outA <- lm(fev ~ height, data=fev, subset=(gender == 'M' & smoking == 'N'))
lm.outB <- lm(fev ~ height, data=fev, subset=(gender == 'M' & smoking == 'Y'))
lm.outC <- lm(fev ~ height, data=fev, subset=(gender == 'F' & smoking == 'N'))
lm.outD <- lm(fev ~ height, data=fev, subset=(gender == 'F' & smoking == 'Y'))
par(las=1)
plot(fev ~ height, data=fev, type="n", xlab="height", ylab="fev")
points(fev ~ height, data=fev, subset=(gender == 'M' & smoking == 'N'), col="blue", lwd=2)
points(fev ~ height, data=fev, subset=(gender == 'M' & smoking == 'Y'), col="green", lwd=2)
points(fev ~ height, data=fev, subset=(gender == 'F' & smoking == 'N'), col="red", lwd=2)
points(fev ~ height, data=fev, subset=(gender == 'F' & smoking == 'Y'), col="purple", lwd=2)
abline(lm.outA$coef, col="blue", lty=2, lwd=2)
abline(lm.outB$coef, col="green", lty=2, lwd=2)
abline(lm.outC$coef, col="red", lty=2, lwd=2)
abline(lm.outD$coef, col="purple", lty=2, lwd=2)

plot(fev)
```

## (b)
Fit your statistical models, and select the parameters for your final model.

``` {r}
lm.A <- lm(fev ~ gender + height + smoking, data = fev)
```




